\bf Faster Neural Machine Translation Inference

### 2018-05-11 fast-beam/fast-beam.tex
use requireProb

These changes do not reduce the asymtotic runtime of our algorithm, which remains at $\mathcal{O}(|p|)$, but it does bring the number of iterations over $p$ down from 5 to 1. In practise, this has a significant affect on inference speed.

>>>>

These changes do not reduce the asymptotic runtime of our algorithm, which remains at $\mathcal{O}(|p|)$, but it does bring the number of iterations over $p$ down from 5 to 1. In practise, this has a significant affect on inference speed.
